\renewcommand{\bibname}{References}
\addcontentsline{toc}{chapter}{References}

\begin{thebibliography}{9}
\bibitem{designpatterns} 
Erich Gamma, Richard Helm, Ralph Johnson, John Vlissides (1994).
\textit{Design Patterns: Elements of Reusable Object-Oriented Software}.

\bibitem{dataintensive} 
Martin Kleppmann (2016).
\textit{Designing Data-Intensive Applications: The Big Ideas Behind Reliable, Scalable, and Maintainable Systems}

\bibitem{websitecloud}
Jeffrey Barr (2010).
\textit{Host Your Web Site in the Cloud: Amazon Web Services Made Easy}

\bibitem{mongodb}
Kyle Banker (2011).
\textit{MongoDB in Action}

\bibitem{50rules}
Martin Abbott, Michael Fisher (2011).
\textit{Scalability Rules: 50 Principles for Scaling Web Sites}

\bibitem{rabbitmq}
Alvaro Videla and Jason J. W. Williams. (2012)
\textit{RabbitMQ in Action: Distributed Messaging for Everyone}

% ---------- research papers -------------
\bibitem{trends}
Olston, C., \& Najork, M. (2010).
\textit{Web crawling. Foundations and Trends in Information Retrieval, 4(3), 175-246.}

\bibitem{mercator}
Heydon, A., \& Najork, M. (1999).
\textit{Mercator: A scalable, extensible web crawler.World Wide Web, 2(4), 219-229.}

\bibitem{ubicrawler}
Boldi, P., Codenotti, B., Santini, M., \& Vigna, S. (2004).
\textit{Ubicrawler: A scalable fully distributed web crawler. Software: Practice and Experience, 34(8), 711-726.}

\bibitem{irlbot}
Lee, H. T., Leonard, D., Wang, X., \& Loguinov, D. (2009).
\textit{IRLbot: scaling to 6 billion pages and beyond. ACM Transactions on the Web (TWEB), 3(3), 8.}

\bibitem{multicrawler}
Harth, A., Umbrich, J., \& Decker, S. (2006).
\textit{Multicrawler: A pipelined architecture for crawling and indexing semantic web data. In The Semantic Web-ISWC 2006 (pp. 258-271). Springer Berlin Heidelberg.}

\bibitem{blocks}
Seeger, M. (2010).
\textit{Building blocks of a scalable web crawler. Master's thesis, Stuttgart Media University.}

\bibitem{consisthash}
Karger, D.; Lehman, E.; Leighton, T.; Panigrahy, R.; Levine, M.; Lewin, D. (1997)
\textit{Consistent hashing and random trees: distributed caching protocols for relieving hot spots on the World Wide Web}

\bibitem{lsh}
Malcolm Slaney, Michael Casey (2008)
\textit{Locality-Sensitive Hashing for Finding Nearest Neighbors}

\bibitem{tunnels}
Scott Wiersdorf on system administration, ssh, security, featured
\textit{An Illustrated Guide to SSH Tunnels (2015)}

\bibitem{zookeeper}
Patrick Hunt; Mahadev Konar; Flavio P. Junqueira; Benjamin Reed
\textit{ZooKeeper: Wait-free coordination for Internet-scale systems}

\bibitem{chubby}
Mike Burrows
\textit{The Chubby lock service for loosely-coupled distributed systems}

\bibitem{microservices}
Sam Newman (2015)
\textit{Building Microservices: Designing fine-grained systems}



\bibitem{swheritage}
Roberto Di Cosmo, Stefano Zacchiroli
\textit{Software Heritage: Why and How to Preserve Software Source Code}

\bibitem{cidr}
  V. Fuller, T. Li, J. Yu, K. Varadhan (Sept. 1993)
  \textit{Classless Inter-Domain Routing (CIDR): an Address Assignment and Aggregation Strategy}

\bibitem{dedupe}
  Gurmeet Singh Manku, Arvind Jain, Anish Das Sarma (2007)
  \textit{Detecting Near-Duplicates for Web Crawling}

\bibitem{contentExtract}
  Matthew E. Peters, Dan Lecocq (May, 2013)
  \textit{Content Extraction Using Diverse Feature Sets}

\bibitem{netarchive}
  Scott Kirkpatrick (2009)
  \textit{Architecture of the internet archive}

\bibitem{datasci}
  Monica Rogati (June, 2017)
  \textit{The AI Hierarchy of Needs}

\bibitem{dataengr}
  Maxime Beauchemin (Jan, 2017)
  \textit{The Rise of Data Engineer}

\bibitem{consisthash}
  David Karger, Eric Lehman, Tom Leighton, et al.(1997)
  \textit{Consistent Hashing and Ran‐dom Trees: Distributed Caching Protocols for Relieving Hot Spots on the World Wide Web}

\bibitem{antimicro}
  Chris Richardson
  \textit{Microservices Patterns}

\bibitem{microgeneral}
\url{https://microservices.io/}

\bibitem{docker}
\url{https://www.docker.com/}

\bibitem{aws}
\url{https://aws.amazon.com/}

\end{thebibliography}